Modelling long-term effects of management strategies in mixed fisheries

### 2019-04-10 doc/MSE_MAR_18.tex
worked on discussion

Meanwhile, when constraining both species, the production potential of both stocks was maintained, that is to say the yield curves were unchanged. However, individual quota cobined with the stochastic fisheries catches resulted in lower than intended exploitation rates. The TACs were set so that the total TACs corresponded to the harvest rate that resulted in maximum sustainable yields. The TACs were divided in individual quotas for each fishing vessel. The lower than intended harvest rates were caused by the fact that despite their planning, fishers often exhausted one of the quotas before the other. If discarding is not allowed, then individual fishers must then stop fishing. At the population levels of the two species this resulted in overal cacthes that were lower than the TACs. Such lack of achieving MSY in mixed fisheries with multiple single-species quota has been described elsewhere (xxxx,xxxx,xx), but thereit was attributed to a difference in the life-history characteristics of the different species. Here it is only because of schochasticiyty in catches that is pervasive in all fisheries.DEPENDS ON QUOTA TRADING, AND IF THAT IS POSSIBLE/ HOW GOOD IS MARKET

WHEN MOVING TO MSY HARVEST RATES THERE ARE FEW YEARS WITH REDUCED CATCHES LIKE CLASSICAL MODELS.

The forecasted effects of fisheries management in mixed fisheries result from individual choices by fishers on management and spatial heterogeneity in the resources rather than in differences in biological characestics of the resources. This emphsizes the need for incorporating detailed fishing dynamics. Histrocially, focus of management strategy evaluation has been primarily on managing the population (biological) dynamics of single and multispecies fisheries \cite{Butterworth2007, Dichmont2006b, Punt1999, Punt2009, Smith1999}. Few MSE studies have explicitly incorporated the direct effects of human dimension harvesting on the stocks, although is equally important \cite{Fulton2011}. Human behaviour and decision-making are intrinsic parts of conservation and natural resource management. MSE with explicit human (social) behaviour dimension is increasingly being used \cite{Andersen2010, Ono2018} as fisheries science takes other sources of uncertainty to a greater extent to identify management actions that ensure the sustainability of fisheries.

Our modeling MSE approach use a dynamic state variable model, including fishing location choices and heterogeneous populations, to evaluate the costs and benefits, both economic and in terms of risks to both stock and livelihoods, that resulted in response of adopting a major policy change such as the CFP \cite{CFP2013}. Starting from an overfished mixed fishery under open access conditions but with a landing obligation constraint, where discarding is not allowed, the response of individual effort allocation and the interannual dynamics for both fleet dynamics and quota allocation is counted when adopting MSY objectives while landing all catches. The analysis extended earlier approaches which used short-term state-dependent decision-making models (e.g. \cite{Alzorriz2018, Batsleer2016, Poos2010}) by including the consequent biomass of fish stocks and the management procedure to make its decision on how to respond to the state of the resource. The MSE framework, was thought of as a minimum realistic model \cite{Kell2007, Punt1995}, and included temporal and spatial key processes in the dynamics of two fish populations, the fisheries and a reevaluation of management targets. To keep the model simple, the two fish populations modelled here are exactly the same apart from their spatial distribution difference (Fig. \ref{f:distribution}). As a result, if the landing obligation changes selectivity patterns in the shor-term as predicted in \cite{Alzorriz2018, Batsleer2016}, the present MSE modeling approach allows the evaluation on the reference points for sustainable exploitation in longer terms by explicitly modelling how changes in exploitation rates impact fish populations and yields. ERROR IN DECISION MAKING, NO DISCARING ALLOWED BY FISHERS, AND PERFECT COMPLIANCE TO THIS

>>>>

Meanwhile, when constraining both species, the production potential of both stocks was maintained, that is to say the yield curves were unchanged. However, individual quota cobined with the stochastic fisheries catches resulted in lower than intended exploitation rates. The TACs were set so that the total TACs corresponded to the harvest rate that resulted in maximum sustainable yields. The TACs were divided in individual quotas for each fishing vessel. The lower than intended harvest rates were caused by the fact that despite their planning, fishers often exhausted one of the quotas before the other. If discarding is not allowed, then individual fishers must then stop fishing. At the population levels of the two species this resulted in overal cacthes that were lower than the TACs. Such lack of achieving MSY in mixed fisheries with multiple single-species quota has been described elsewhere \cite{Kempf2016, Rindorf2017, Hilborn2015}, but is generall attributed to differences in life-histories among fished species. In this study, the discrepancy between the intended annual quotas at MSY and realized catches is caused only by schochasticity in the system. This stochasticy in catch rates is observed in most fisheries  \cite{Sampson1988, VanOostenbrugge2004, Smith1980, Bernasconi2015}. It is caused by the complex migration biology and the effects of environmental factors on fish behaviour. A well functioning quota market would allow vessels to swap excess quota for constraining and thus bring realized catches closer to quotas.

The model aimed to evaluate the biological and economic effects of adopting a major policy change such as the CFP \cite{CFP2013}. Starting from an overfished mixed fishery under open access conditions but with a landing obligation, the response of individual effort allocation and the interannual population dynamics are explicitly modeled, while adopting MSY objectives. The analysis extended earlier approaches that used short-term state-dependent decision-making models (e.g. \cite{Alzorriz2018, Batsleer2016, Poos2010}) by including interannual population dynamics of fish stocks, and a management procedure that mimics the decisions of a management system. Such an MSE framework was thought of as a minimum realistic model \cite{Kell2007, Punt1995}. To keep the outcomes of the model simple, and to show the implications of the fishing effort allocation, the two fish populations modelled here are exactly the same apart from their spatial distribution difference (Fig. \ref{f:distribution}). As a result, if the landing obligation changes selectivity patterns in the short-term as predicted in \cite{Alzorriz2018, Batsleer2016}, the present MSE modeling approach allows the evaluation on the reference points for sustainable exploitation in longer terms by explicitly modelling how changes in exploitation rates impact fish populations and yields. ERROR IN DECISION MAKING, NO DISCARING ALLOWED BY FISHERS, AND PERFECT COMPLIANCE TO THIS

The forecasted effects of fisheries management in mixed fisheries result from spatial heterogeneity in resources and fishers adaptive behaviour. This emphasizes that human behaviour and decision-making are intrinsic parts of conservation and natural resource management and the need for incorporating detailed fishing dynamics in management strategy evaluation. Historically, the focus of management strategy evaluation has been primarily on population dynamics in single and multispecies fisheries \cite{Butterworth2007, Dichmont2006b, Punt1999, Punt2009, Smith1999, Punt2016}. Explicitly incorporating direct effects of human behaviour of those who harvest stocks is equally important \cite{Fulton2011,Milner-Gulland2012}, but relatively few studies have attempted this \cite{Andersen2010, Ono2018}. Our MSE that links a dynamic state variable model for fisher behavior to a multi-species age structured model provides an alternative to those approaches.
